Models

### 2021-08-04 analysis/05_model_metrics.Rmd
Fix issue with assigning significance

  study_ests <- broom.mixed::tidy(model, effects="ran_vals") %>%
    filter(group == filter_name, term == "year_scaled") %>% 
    select(-c(effect, group, term)) %>%
    #rename({{ model_id }} := level, cond.std.error = std.error, cond.estimate = estimate) %>%
    rename(cond.std.error = std.error, cond.estimate = estimate) %>%
    mutate(estimate = cond.estimate + year_scaled_est,
      cond.var = cond.std.error*cond.std.error, 
           var = cond.var + year_scaled_var,
           std.error = sqrt(var),
           upr.ci = estimate + (2*std.error),
           lwr.ci = estimate - (2*std.error),
           sig = case_when(
             lwr.ci < 0 & upr.ci > 0 ~ TRUE,
             TRUE ~ FALSE
           ),
      metric = metric,
      model_id = model_id)
}

@@

study_slopes <- pmap_dfr(model_df, get_study_slopes)

study_slopes_wide <- study_slopes %>%
  filter(model_id == "base") %>%
  select(study_id = level, metric, estimate) %>%
  pivot_wider(names_from = "metric", values_from = "estimate")
```

@@

#And how many were significant for all but Jaccard?
study_slopes %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "S")) %>% 
  group_by(study_id) %>% filter(sum(sig) == 4) %>% pull(study_id) %>% 
  n_distinct()

#Breakdown of relationship between functional richness and species richness
s_sig <- study_slopes %>% filter(metric == "S", sig == TRUE) %>% pull(study_id) %>% unique()
s_sig_not_fric <- study_slopes %>% 
  filter(study_id %in% s_sig, metric == "FRic", sig == FALSE) %>% 
  pull(study_id) %>%
  unique()

both_sig <- study_slopes %>% 
  filter(study_id %in% s_sig, metric == "FRic", sig == TRUE) %>%
  pull(study_id)

both_pos
fric_pos
s_pos_fric_neg <- study_slopes %>%
  filter(study_id %in% both_sig) %>% 
  group_by(study_id) %>%
  filter(sum(sign(estimate)) == 0)

>>>>

  study_ests <- broom.mixed::tidy(model, effects="ran_vals") %>%
    filter(group == filter_name, term == "year_scaled") %>% 
    select(-c(effect, group, term)) %>%
    #rename({{ model_id }} := level, cond.std.error = std.error, cond.estimate = estimate) %>%
    rename(cond.std.error = std.error, cond.estimate = estimate) %>%
    mutate(estimate = cond.estimate + year_scaled_est,
      cond.var = cond.std.error*cond.std.error, 
           var = cond.var + year_scaled_var,
           std.error = sqrt(var),
           upr.ci = estimate + (2*std.error),
           lwr.ci = estimate - (2*std.error),
           sig = case_when(
             lwr.ci < 0 & upr.ci > 0 ~ FALSE,
             TRUE ~ TRUE
           ),
      metric = metric,
      model_id = model_id)
}

@@

re_slopes <- pmap_dfr(model_df, get_study_slopes)

study_slopes <- re_slopes %>% 
  filter(model_id == "base") %>%
  rename(study_id = level)

study_slopes_wide <- study_slopes %>%
  select(study_id, metric, estimate) %>%
  pivot_wider(names_from = "metric", values_from = "estimate")
```

@@

#And which studies were they?
study_slopes %>% 
  filter(sig == TRUE) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S")) %>% 
  select(study_id, metric) %>%
  distinct()

#Which were significant for multiple metrics?
study_slopes %>% 
  filter(sig == TRUE) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S")) %>% 
  group_by(study_id) %>%
  filter(n() > 1) %>%
  select(study_id, metric)
```

```{r}
# #And how many were significant for all but Jaccard?
# study_slopes %>% 
#   filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "S")) %>% 
#   group_by(study_id) %>% filter(sum(sig) == 4) %>% pull(study_id) %>% 
#   n_distinct()
# 
# #Breakdown of relationship between functional richness and species richness
# s_sig <- study_slopes %>% filter(metric == "S", sig == TRUE) %>% pull(study_id) %>% unique()
# s_sig_not_fric <- study_slopes %>% 
#   filter(study_id %in% s_sig, metric == "FRic", sig == FALSE) %>% 
#   pull(study_id) %>%
#   unique()
# 
# both_sig <- study_slopes %>% 
#   filter(study_id %in% s_sig, metric == "FRic", sig == TRUE) %>%
#   pull(study_id)
# 
# both_pos
# fric_pos
# s_pos_fric_neg <- study_slopes %>%
#   filter(study_id %in% both_sig) %>% 
#   group_by(study_id) %>%
#   filter(sum(sign(estimate)) == 0)
